The transition redshift as a probe of reionization

### 2019-08-09 paper/ms.tex
Add beginning of intro

\section{Introduction}
The introduction.

>>>>

\section{Introduction}
The redshifted 21~cm line contains a great deal of information about the
structure and evolution of the Epoch of Reionization (EoR). Once measured at
$z\sim6\textup{--}12$, it should reveal the nature of the formation of the
first stars, galaxies, and black holes, as well as the large-scale structure
of the Universe at high redshift \citep{2013fgu..book.....L}. While
instruments have reached the sensitivity necessary to detect the signal during
the EoR, issues of foreground contamination and instrumental artifacts have so
far prevented the success of such efforts. Only upper limits have been placed
on the amplitude of the 21~cm fluctuations \citep[e.g.][]{2013MNRAS.433..639P,
2014PhRvD..89b3002D, 2016ApJ...833..102B, 2017ApJ...838...65P}.
